Multiple quantum NMR in solids as a method of determination of Wigner--Yanase skew information

### 2021-06-02 manuscript.tex
Fix 'b' to 'beta' in figures and captions

\begin{figure}
	\includegraphics[width=0.95\linewidth]{zigzag_entangled_spins_by_temp}
	\caption{
		The dependence of the number $N_\mathrm{ent}$ of the entangled spins on the parameter $b$ (the inverse temperature) for zigzag chains consisting of six spins.
	}
	\label{fig:3}
\end{figure}

>>>>

\begin{figure}
	\includegraphics[width=0.95\linewidth]{zigzag_entangled_spins_by_temp}
	\caption{
		The dependence of the number $N_\mathrm{ent}$ of the entangled spins on the parameter $\beta$ (the inverse temperature) for zigzag chains consisting of six spins.
	}
	\label{fig:3}
\end{figure}
